
\documentclass[]{deedy-resume-openfont}


\begin{document}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     LAST UPDATED DATE
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     TITLE NAME
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%


\namesection{Krishna}{Jangid}{ \urlstyle{same}\url{https://github.com/jangidkrishna} \\
\href{mailto:jangid.krishna01@gmail.com}{jangid.krishna01@gmail.com} | 7358228200
}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     COLUMN ONE
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{minipage}[t]{0.33\textwidth}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     EDUCATION
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Education}

\subsection{SRM IST}
\descript{BTech in Computer Science}
\location{Expected May 2020 | Chennai, TN }
\sectionsep

\sectionsep

\subsection{Jayshree Periwal}
\descript{High School}
\descript{Majored in Science and Maths}
\location{Grad. May 2016 |  Jaipur, RAJ}
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     LINKS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Links}
Github:// \href{https://github.com/jangidkrishna}{\custombold{jangidkrishna}} \\
Twitter://  \href{https://twitter.com/imkrishnajangid}{\custombold{@imkrishnajangid}} \\

\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     COURSEWORK
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Coursework}


\subsection{Undergraduate}
MatLab\\
Micro Processor, Micro Controller \\
Data Structure \\
Algorithm Design and Development \\
Unix Tools and Scripting \\
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     SKILLS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Skills}
\subsection{Programming}
\location{Over 5000 lines:}
Solidity \textbullet{}   Shell \textbullet{} GOLANG \textbullet{} C++ \\
\location{Over 1000 lines:}
C \textbullet{} Python \textbullet{} JavaScript  \\
\location{Familiar:}
Hadoop \textbullet{} MySQL
\sectionsep

\subsection{Languages}
\textbullet{} English \\
\textbullet{} French(A2 Level) \\
\textbullet{} Hindi \\
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     COLUMN TWO
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\end{minipage}
\hfill
\begin{minipage}[t]{0.66\textwidth}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     EXPERIENCE
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Experience}

\runsubsection{Next Tech Lab}
\descript{| Researcher }
\location{August 2017 - Present | Chennai, TN}
\vspace{\topsep} % Hacky fix for awkward extra vertical space
\begin{tightemize}
\item I am working as an  in Satoshi Lab (Cryptocurrency lab) a sub-domain of Next Tech Lab, currently working on Blockchains, Dapps, encryption algorithms and cryptocurrencies.
\end{tightemize}
\sectionsep

\runsubsection{Innovana ThinkLabs Ltd}
\descript{| Intern }
\location{June 2018 | Jaipur, RAJ}
\vspace{\topsep} % Hacky fix for awkward extra vertical space
\begin{tightemize}
\item I was worked on the live development project (ITL web browser).
\end{tightemize}
\sectionsep

\runsubsection{Natsav}
\descript{| Junior System Administrator }
\location{Jaipur, RAJ}
\begin{tightemize}
\item I was responsible for the administrative duties, automation and general order of the servers and managed security of the servers.

\end{tightemize}
\sectionsep


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     RESEARCH
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{projects}
\runsubsection{\href{https://github.com/jangidkrishna/0xSHG}{0xSHG}}
\descript{| "0" interest loans for rural micro-finance}
\location{Nov 2017 }
My Team and I've created an Aadhar-linked digital pan-Indian capital-pooling Decentralized App (Dapp) . Through this network, maximum possilbe microloan requests are fully funded with 0 percentage interest (least request satisfied first) and the reserve wealth is re-distributed into the system.
\sectionsep

\runsubsection{MetaChain}
\descript{| Self-owning assets, that can function financially with complete autonomy}
\location{Feb 2018}
A self-owning asset. The asset itself has legal and financial responsibility of itself, and can verify certificates itself. My Team and I've achieve this using smart contracts and IoT.
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     AWARDS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Awards}
\begin{tabular}{rll}
2018	     & 4\textsuperscript{th}  & BTS Bengluru Blockchain Hackathon\\
2017	     & Accel Prize  & Proffer Blockchain Hackathon\\
2017	     & 1\textsuperscript{st}  & Hackerrank Bash Shell problems\\
\end{tabular}
\sectionsep

\section{Certifications}
\begin{tabular}{rll}
2017	     & Red Hat Certified Sys Admin Openstack Admin \\
2017	     & Red Hat Certified Engineer\\
2016	     & Red Hat Certified Sys Admin\\
\end{tabular}
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     SOCIETIES
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Societies}

\begin{tabular}{rll}
2018   & National & ACM Students Chapter\\
\end{tabular}
\sectionsep

\end{minipage}
\end{document}  \documentclass[]{article}
